---
title: "The overlap between social isolation and mental health problems: ACE herogeniety model (sex differences)" 
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: flatly
    code_folding: show
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      prompt = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      results = 'markup')

options(bitmapType = 'quartz') # to render fonts better
```

```{r Clear global environment, include=FALSE}
remove(list = ls())
```

```{r Load packages, include=FALSE}
library(knitr)
library(haven)
library(psych)   
library(bestNormalize)
library(OpenMx)
library(tidyr)
library(tidyverse)
library(dplyr)     # conflicts with tidyverse for e.g. rename and row_number
```

# Source functions

```{r source functions, include=FALSE}
source("isolation_mhealth_functions.R")
```

# Read in data

```{r source the data file path, include=FALSE}
# source raw data directory
source("../isolation_mentalhealth_data_path.R")
```

```{r read in dta data file, include=FALSE}
dat.raw <- read_dta(paste0(data_path_raw, "Katie_23Sep22.dta"))
colnames(dat.raw)
```

### Column names

```{r select variables needed}
dat <- dat.raw %>%
  dplyr::select(
         atwinid,
         btwinid,
         familyid,
         rorderp5,
         torder,
         zygosity,
         sampsex,
         sisoe12,
         sisoy12,
         masce12,     # anxiety
         mascy12,   
         cdie12,      # depression
         cdiy12,
         conec12,     # antisocial behaviour / conduct disorder
         conyc12,
         psysympe12,  # psychosis - why is this not the tot scale variable - to give more variation?
         psysympy12,
         socisoe18,
         socisoy18,
         gadsxe18,    # anxiety
         gadsxy18,
         mdesxe18,    # depression
         mdesxy18,
         cdsxe18,     # antisocial behaviour / conduct disorder
         cdsxy18,
         psyexpe18,   # psychotic experiences
         psyexpy18
  )

colnames(dat)
```

### Recode variables into factors {.tabset .tabset-fade}

#### Sex

```{r recode sex}
dat <- dat %>%
  mutate(
    sex = 
      recode_factor(as_factor(sampsex),
        "1" = "Male",
        "2" = "Female"))

table(dat$sex)
```

#### Zygosity

```{r recode zygosity}
dat <- dat %>%
  mutate(
    zygosity = 
      recode_factor(as_factor(zygosity),
        "1" = "MZ",
        "2" = "DZ"))
table(dat$zygosity)
```

### Convert variables to numeric

```{r create numeric isolation variables}
dat <- dat %>%
  mutate(
    sisoe12 = as.numeric(sisoe12),
    sisoy12 = as.numeric(sisoy12),
    masce12 = as.numeric(masce12),       # anxiety
    mascy12 = as.numeric(mascy12),   
    cdie12 = as.numeric(cdie12),         # depression
    cdiy12 = as.numeric(cdiy12),
    conec12 = as.numeric(conec12),       # antisocial behaviour / conduct disorder
    conyc12 = as.numeric(conyc12),
    psysympe12 = as.numeric(psysympe12), # psychosis - why is this not the tot scale variable - to give more variation?
    psysympy12 = as.numeric(psysympy12),
    socisoe18 = as.numeric(socisoe18),
    socisoy18 = as.numeric(socisoy18),
    gadsxe18 = as.numeric(gadsxe18),     # anxiety
    gadsxy18 = as.numeric(gadsxy18),
    mdesxe18 = as.numeric(mdesxe18),     # depression
    mdesxy18 = as.numeric(mdesxy18),
    cdsxe18 = as.numeric(cdsxe18),       # antisocial behaviour / conduct disorder
    cdsxy18 = as.numeric(cdsxy18),
    psyexpe18 = as.numeric(psyexpe18),   # psychotic experiences
    psyexpy18 = as.numeric(psyexpy18)
  ) %>%
  select(                                # remove variables not needed
    -c(sampsex)
  )
```

# Variable lists

```{r select variables - raw}
# social isolation
selvars_si12 <- c("sisoe12", "sisoy12")
selvars_si18 <- c("socisoe18", "socisoy18")

# anxiety
selvars_anx12 <- c("masce12", "mascy12")
selvars_anx18 <- c("gadsxe18", "gadsxy18")

# depression
selvars_dep12 <- c("cdie12", "cdiy12")
selvars_dep18 <- c("mdesxe18", "mdesxy18")

# conduct
selvars_con12 <- c("conec12", "conyc12")
selvars_con18 <- c("cdsxe18", "cdsxy18")

# psychosis
selvars_psy12 <- c("psysympe12", "psysympy12")
selvars_psy18 <- c("psyexpe18", "psyexpy18")

# all 
selvars <- c("sisoe12", "masce12", "cdie12", "conec12",  "psysympe12", "socisoe18", "gadsxe18", "mdesxe18", "cdsxe18", "psyexpe18",
             "sisoy12", "mascy12", "cdiy12", "conyc12", "psysympy12",  "socisoy18", "gadsxy18", "mdesxy18", "cdsxy18","psyexpy18")
```

```{r select variables - standardised}
# social isolation
selvars_si12_z_score <- c("z_score_sisoe12", "z_score_sisoy12")
selvars_si18_z_score <- c("z_score_socisoe18", "z_score_socisoy18")

# anxiety
selvars_anx12_z_score <- c("z_score_masce12", "z_score_mascy12")
selvars_anx18_z_score <- c("z_score_gadsxe18", "z_score_gadsxy18")

# depression
selvars_dep12_z_score <- c("z_score_cdie12", "z_score_cdiy12")
selvars_dep18_z_score <- c("z_score_mdesxe18", "z_score_mdesxy18")

# conduct
selvars_con12_z_score <- c("z_score_conec12", "z_score_conyc12")
selvars_con18_z_score <- c("z_score_cdsxe18", "z_score_cdsxy18")

# psychosis
selvars_psy12_z_score <- c("z_score_psysympe12", "z_score_psysympy12")
selvars_psy18_z_score <- c("z_score_psyexpe18", "z_score_psyexpy18")
```

```{r select variables - normalised}
# social isolation
selvars_si12norm <- c("sisoe12norm", "sisoy12norm")
selvars_si18norm <- c("socisoe18norm", "socisoy18norm")

# anxiety
selvars_anx12norm <- c("masce12norm", "mascy12norm")
selvars_anx18norm <- c("gadsxe18norm", "gadsxy18norm")

# depression
selvars_dep12norm <- c("cdie12norm", "cdiy12norm")
selvars_dep18norm <- c("mdesxe18norm", "mdesxy18norm")

# conduct
selvars_con12norm <- c("conec12norm", "conyc12norm")
selvars_con18norm <- c("cdsxe18norm", "cdsxy18norm")

# psychosis
selvars_psy12norm <- c("psysympe12norm", "psysympy12norm")
selvars_psy18norm <- c("psyexpe18norm", "psyexpy18norm")

# all 
selvars_norm <- c("sisoe12norm", "masce12norm", "cdie12norm", "conec12norm", "psysympe12norm", "socisoe18norm", "gadsxe18norm", "mdesxe18norm", "cdsxe18norm", "psyexpe18norm",
                  "sisoy12norm", "mascy12norm", "cdiy12norm", "conyc12norm", "psysympy12norm", "socisoy18norm", "gadsxy18norm", "mdesxy18norm", "cdsxy18norm", "psyexpy18norm")

# all with non-normalised - not in the twin modelling specific order here only used to standardise all variables at once
selvars_norm_all <- c("sisoe12", "sisoy12", "masce12", "mascy12", "cdie12", "cdiy12", "conec12", "conyc12", "psysympe12", "psysympy12", 
                      "socisoe18", "socisoy18", "gadsxe18", "gadsxy18", "mdesxe18", "mdesxy18", "cdsxe18", "cdsxy18", "psyexpe18", "psyexpy18",
                      "sisoe12norm", "sisoy12norm", "masce12norm", "mascy12norm", "cdie12norm", "cdiy12norm", "conec12norm", "conyc12norm", "psysympe12norm", "psysympy12norm", 
                      "socisoe18norm", "socisoy18norm", "gadsxe18norm", "gadsxy18norm", "mdesxe18norm", "mdesxy18norm", "cdsxe18norm", "cdsxy18norm", "psyexpe18norm", "psyexpy18norm")
```

```{r select variables - standardised and normalised}
# social isolation
selvars_si12_z_score_norm <- c("z_score_sisoe12norm", "z_score_sisoy12norm")
selvars_si18_z_score_norm <- c("z_score_socisoe18norm", "z_score_socisoy18norm")

# anxiety
selvars_anx12_z_score_norm <- c("z_score_masce12norm", "z_score_mascy12norm")
selvars_anx18_z_score_norm <- c("z_score_gadsxe18norm", "z_score_gadsxy18norm")

# depression
selvars_dep12_z_score_norm <- c("z_score_cdie12norm", "z_score_cdiy12norm")
selvars_dep18_z_score_norm <- c("z_score_mdesxe18norm", "z_score_mdesxy18norm")

# conduct
selvars_con12_z_score_norm <- c("z_score_conec12", "z_score_conyc12")
selvars_con18_z_score_norm <- c("z_score_cdsxe18norm", "z_score_cdsxy18norm")

# psychosis
selvars_psy12norm_z_score_norm <- c("z_score_psysympe12norm", "z_score_psysympy12norm")
selvars_psy18norm_z_score_norm <- c("z_score_psyexpe18norm", "z_score_psyexpy18norm")
```

```{r select variables - normalised and regressed sex}
# social isolation
selvars_si12norm_reg <- c("sisoe12norm_reg", "sisoy12norm_reg")
selvars_si18norm_reg <- c("socisoe18norm_reg", "socisoy18norm_reg")

# anxiety
selvars_anx12norm_reg <- c("masce12norm_reg", "mascy12norm_reg")
selvars_anx18norm_reg <- c("gadsxe18norm_reg", "gadsxy18norm_reg")

# depression
selvars_dep12norm_reg <- c("cdie12norm_reg", "cdiy12norm_reg")
selvars_dep18norm_reg <- c("mdesxe18norm_reg", "mdesxy18norm_reg")

# conduct
selvars_con12norm_reg <- c("conec12norm_reg", "conyc12norm_reg")
selvars_con18norm_reg <- c("cdsxe18norm_reg", "cdsxy18norm_reg")

# psychosis
selvars_psy12norm_reg <- c("psysympe12norm_reg", "psysympy12norm_reg")
selvars_psy18norm_reg <- c("psyexpe18norm_reg", "psyexpy18norm_reg")

# all 
selvars_norm_reg <- c("sisoe12norm_reg", "masce12norm_reg", "cdie12norm_reg", "conec12norm_reg", "psysympe12norm_reg", "socisoe18norm_reg", "gadsxe18norm_reg", "mdesxe18norm_reg", "cdsxe18norm_reg", "psyexpe18norm_reg",
                  "sisoy12norm_reg", "mascy12norm_reg", "cdiy12norm_reg", "conyc12norm_reg", "psysympy12norm_reg", "socisoy18norm_reg", "gadsxy18norm_reg", "mdesxy18norm_reg", "cdsxy18norm_reg", "psyexpy18norm_reg")

# all with non-norm_regalised - not in the twin modelling specific order here only used to standardise all variables at once
selvars_norm_reg_all <- c("sisoe12", "sisoy12", "masce12", "mascy12", "cdie12", "cdiy12", "conec12", "conyc12", "psysympe12", "psysympy12", 
                      "socisoe18", "socisoy18", "gadsxe18", "gadsxy18", "mdesxe18", "mdesxy18", "cdsxe18", "cdsxy18", "psyexpe18", "psyexpy18",
                      "sisoe12norm_reg", "sisoy12norm_reg", "masce12norm_reg", "mascy12norm_reg", "cdie12norm_reg", "cdiy12norm_reg", "conec12norm_reg", "conyc12norm_reg", "psysympe12norm_reg", "psysympy12norm_reg", 
                      "socisoe18norm_reg", "socisoy18norm_reg", "gadsxe18norm_reg", "gadsxy18norm_reg", "mdesxe18norm_reg", "mdesxy18norm_reg", "cdsxe18norm_reg", "cdsxy18norm_reg", "psyexpe18norm_reg", "psyexpy18norm_reg")
```

# Data prep

## Skewness

```{r histograms}
# isolation
hist(dat$sisoe12)    # not normal
hist(dat$socisoe18)  # not normal
# anxiety
hist(dat$masce12)    # normal
hist(dat$gadsxe18)   # not normal
# depression
hist(dat$cdie12)     # not normal
hist(dat$mdesxe18)   # not normal
# conduct
hist(dat$conec12)    # not normal
hist(dat$cdsxe18)    # not normal
# psychosis
hist(dat$psysympe12) # not normal
hist(dat$psyexpe18)  # not normal
```

## Rank transformation

Almost all variables are non-normal. We will use the van der Waerden's rank-based transformation as used in [Rimfeld et al 2021](https://acamh.onlinelibrary.wiley.com/doi/full/10.1002/jcv2.12053). For analyses using transformed data, they conducted the van der Waerden transformation prior to residualizing for age and sex as recommended by [Pain et al. 2018](https://www.nature.com/articles/s41431-018-0159-6).  

I will transform all variables to get the normalised estimate.

```{r rank transform variables elder variables}
# isolation age 12
sisoe12_n <- bestNormalize(dat$sisoe12)    # select the type of transformation needed
dat$sisoe12norm <- predict(sisoe12_n)      # create normalised variable
hist(dat$sisoe12norm)                  
summary(dat$sisoe12norm)

# isolation age 18
socisoe18_n <- bestNormalize(dat$socisoe18)    
dat$socisoe18norm <- predict(socisoe18_n)  
hist(dat$socisoe18norm)                  
summary(dat$socisoe18norm)

# anxiety age 12 - wont actually use this as it's already normally distributed
masce12_n <- bestNormalize(dat$masce12)    
dat$masce12norm <- predict(masce12_n)  
hist(dat$masce12norm)                  
summary(dat$masce12norm)

# anxiety age 18
gadsxe18_n <- bestNormalize(dat$gadsxe18)    
dat$gadsxe18norm <- predict(gadsxe18_n)  
hist(dat$gadsxe18norm)                  
summary(dat$gadsxe18norm)

# depression age 12
cdie12_n <- bestNormalize(dat$cdie12)    
dat$cdie12norm <- predict(cdie12_n)  
hist(dat$cdie12norm)                  
summary(dat$cdie12norm)

# depression age 18
mdesxe18_n <- bestNormalize(dat$mdesxe18)    
dat$mdesxe18norm <- predict(mdesxe18_n)  
hist(dat$mdesxe18norm)                  
summary(dat$mdesxe18norm)

# conduct age 12
conec12_n <- bestNormalize(dat$conec12)    
dat$conec12norm <- predict(conec12_n)  
hist(dat$conec12norm)                  
summary(dat$conec12norm)

# conduct age 18
cdsxe18_n <- bestNormalize(dat$cdsxe18)    
dat$cdsxe18norm <- predict(cdsxe18_n)  
hist(dat$cdsxe18norm)                  
summary(dat$cdsxe18norm)

# psychosis age 12
psysympe12_n <- bestNormalize(dat$psysympe12)    
dat$psysympe12norm <- predict(psysympe12_n)  
hist(dat$psysympe12norm)                  
summary(dat$psysympe12norm)

# psychosis age 18
psyexpe18_n <- bestNormalize(dat$psyexpe18)    
dat$psyexpe18norm <- predict(psyexpe18_n)  
hist(dat$psyexpe18norm)                  
summary(dat$psyexpe18norm)
```

```{r rank transform variables younger variables}
# isolation age 12
sisoy12_n <- bestNormalize(dat$sisoy12)    # select the type of transformation needed
dat$sisoy12norm <- predict(sisoy12_n)  # create normalised variable
hist(dat$sisoy12norm)                  
summary(dat$sisoy12norm)

# isolation age 18
socisoy18_n <- bestNormalize(dat$socisoy18)    
dat$socisoy18norm <- predict(socisoy18_n)  
hist(dat$socisoy18norm)                  
summary(dat$socisoy18norm)

# anxiety age 12 - wont actually use this as it's already normally distributed
mascy12_n <- bestNormalize(dat$mascy12)    
dat$mascy12norm <- predict(mascy12_n)  
hist(dat$mascy12norm)                  
summary(dat$mascy12norm)

# anxiety age 18
gadsxy18_n <- bestNormalize(dat$gadsxy18)    
dat$gadsxy18norm <- predict(gadsxy18_n)  
hist(dat$gadsxy18norm)                  
summary(dat$gadsxy18norm)

# depression age 12
cdiy12_n <- bestNormalize(dat$cdiy12)    
dat$cdiy12norm <- predict(cdiy12_n)  
hist(dat$cdiy12norm)                  
summary(dat$cdiy12norm)

# depression age 18
mdesxy18_n <- bestNormalize(dat$mdesxy18)    
dat$mdesxy18norm <- predict(mdesxy18_n)  
hist(dat$mdesxy18norm)                  
summary(dat$mdesxy18norm)

# conduct age 12
conyc12_n <- bestNormalize(dat$conyc12)    
dat$conyc12norm <- predict(conyc12_n)  
hist(dat$conyc12norm)                  
summary(dat$conyc12norm)

# conduct age 18
cdsxy18_n <- bestNormalize(dat$cdsxy18)    
dat$cdsxy18norm <- predict(cdsxy18_n)  
hist(dat$cdsxy18norm)                  
summary(dat$cdsxy18norm)

# psychosis age 12
psysympy12_n <- bestNormalize(dat$psysympy12)    
dat$psysympy12norm <- predict(psysympy12_n)  
hist(dat$psysympy12norm)                  
summary(dat$psysympy12norm)

# psychosis age 18
psyexpy18_n <- bestNormalize(dat$psyexpy18)    
dat$psyexpy18norm <- predict(psyexpy18_n)  
hist(dat$psyexpy18norm)                  
summary(dat$psyexpy18norm)
```

## Regress out sex

We first normalised the twin variables, then regress out sex. We don't regress out age here as all twins were measured as close to thir birthday as possible. 

```{r Regress out age and sex}
# twin 1 - elder
## isolation
dat$sisoe12norm_reg <- (resid(lm(data = dat, sisoe12norm ~ sex, na.action = na.exclude))) 
dat$socisoe18norm_reg <- (resid(lm(data = dat, socisoe18norm ~ sex, na.action = na.exclude)))
## anxiety
dat$masce12norm_reg <- (resid(lm(data = dat, masce12norm ~ sex, na.action = na.exclude)))
dat$gadsxe18norm_reg <- (resid(lm(data = dat, gadsxe18norm ~ sex, na.action = na.exclude)))
## depression
dat$cdie12norm_reg <- (resid(lm(data = dat, cdie12norm ~ sex, na.action = na.exclude)))
dat$mdesxe18norm_reg <- (resid(lm(data = dat, mdesxe18norm ~ sex, na.action = na.exclude)))
## conduct
dat$conec12norm_reg <- (resid(lm(data = dat, conec12norm ~ sex, na.action = na.exclude)))
dat$cdsxe18norm_reg <- (resid(lm(data = dat, cdsxe18norm ~ sex, na.action = na.exclude)))
## psychosis
dat$psysympe12norm_reg <- (resid(lm(data = dat, psysympe12norm ~ sex, na.action = na.exclude)))
dat$psyexpe18norm_reg <- (resid(lm(data = dat, psyexpe18norm ~ sex, na.action = na.exclude)))

# twin 2 - younger
## isolation
dat$sisoy12norm_reg <- (resid(lm(data = dat, sisoy12norm ~ sex, na.action = na.exclude))) 
dat$socisoy18norm_reg <- (resid(lm(data = dat, socisoy18norm ~ sex, na.action = na.exclude)))
## anxiety
dat$mascy12norm_reg <- (resid(lm(data = dat, mascy12norm ~ sex, na.action = na.exclude)))
dat$gadsxy18norm_reg <- (resid(lm(data = dat, gadsxy18norm ~ sex, na.action = na.exclude)))
## depression
dat$cdiy12norm_reg <- (resid(lm(data = dat, cdiy12norm ~ sex, na.action = na.exclude)))
dat$mdesxy18norm_reg <- (resid(lm(data = dat, mdesxy18norm ~ sex, na.action = na.exclude)))
## conduct
dat$conyc12norm_reg <- (resid(lm(data = dat, conyc12norm ~ sex, na.action = na.exclude)))
dat$cdsxy18norm_reg <- (resid(lm(data = dat, cdsxy18norm ~ sex, na.action = na.exclude)))
## psychosis
dat$psysympy12norm_reg <- (resid(lm(data = dat, psysympy12norm ~ sex, na.action = na.exclude)))
dat$psyexpy18norm_reg <- (resid(lm(data = dat, psyexpy18norm ~ sex, na.action = na.exclude)))
```

## Standardising

Create *z scores* for all variables. 

```{r scale variables and combine to MZ dataset}
# create a scaled version of the continuous variables - z scores for all variables
scaled_continuous_data <- as.data.frame(scale(dat[selvars_norm_all], center = TRUE, scale = TRUE))

# rename variables to show that they are z scores 
colnames(scaled_continuous_data) <- paste0("z_score_", colnames(scaled_continuous_data))

# combine the scaled data to the main dataset for  and DZ twins
dat <- cbind(dat, scaled_continuous_data)

colnames(dat)
```

## Create twin dataset

To remove the double entry in the data, we will remove everyone who has a "random twin order" variable of 0. This will then remove any birth order effects. 

```{r remove one twin pair row}
dat.twin <- dat %>% filter(rorderp5 == "1")
```

```{r datasets for MZ and DZ}
dat.twin.MZ <- dat.twin %>% filter(zygosity == "MZ")
dat.twin.DZ <- dat.twin %>% filter(zygosity == "DZ")

# male only
dat.twin.MZm <- dat.twin.MZ %>% filter(sex == "Male")
dat.twin.DZm <- dat.twin.DZ %>% filter(sex == "Male")
# female only
dat.twin.MZf <- dat.twin.MZ %>% filter(sex == "Female")
dat.twin.DZf <- dat.twin.DZ %>% filter(sex == "Female")
```

## Summary of MZ and DZ data

### Overall

```{r describe MZ and DZ data}
MZ_summary <- describe(dat.twin.MZ, 
                       skew = FALSE, 
                       range = FALSE)

DZ_summary <- describe(dat.twin.DZ, 
                       skew = FALSE, 
                       range = FALSE)
```

### MZ correlations

```{r MZ matrices}
# covariance matrix
covar.mz <- cov(dat.twin.MZ[, selvars], use = "complete")
# correlation matrix (standardized covariance)
cor.mz <- cor(dat.twin.MZ[, selvars], use = "complete")
# round(cor.mz, 3)
```

### DZ correlations

```{r DZ matrices}
# covariance matrix
covar.dz <- cov(dat.twin.DZ[, selvars], use = "complete")
# correlation matrix (standardized covariance)
cor.dz <- cor(dat.twin.DZ[, selvars], use = "complete")
# round(cor.dz, 3)
```

# Heterogeneity ACE model

This model tests whether genes and environment influence a trait to a different degree in males and females - i.e. do they show quantitative sex differences. 

Sex-limited expression of genetic or environmental factors occurs in two basic forms. First, the effects of a factor may be larger on one sex than on another, which is known as *scalar sex limitation*. Second, some factors may have an effect on one sex but not on the other, which is called nonscalar sex limitation. In the classical twin study, scalar sex- limited effects cause same-sex male and same-sex female twin correlations to differ (Neale, Røysamb, and Jacobson, 2006). 

## Specify

This model will be applied to all variables at age 12 and 18 - social isolation, anxiety, depression, conduct disorder, psychosis. 

```{r number of variables (phenotypes)}
# number of variables
nv <- 1    					      # number of variables 
ntv <- nv*2 				      # number of twin variables

# default optimizer  
mxOption(NULL, "Default optimizer", "CSOLNP")
```

```{r start values}
# start values
svM	  <- c(rep(0.7, ntv))	  # means               
svSD  <- c(rep(1.1, ntv))   # standard deviations
svRmz <- c(0.3)             # correlations for MZ
svRdz <- c(0.15)            # correlations for DZ 

rowVars	<- rep('Vars', nv)
colVars	<- rep(c('h2', 'c2', 'e2'), each = nv)
```

```{r specify quantitative heterogeneity ACE model}
# Matrix & Algebra for expected means vector
MeanM		<- mxMatrix(type = "Full", nrow = 1, ncol = nv, free = TRUE, values = 0, label = "meanm", name = "Mm")
MeanMM	<- mxAlgebra(expression = cbind(Mm, Mm), name = "expMeanm")
MeanF		<- mxMatrix(type = "Full", nrow = 1, ncol = nv, free = TRUE, values = 0, label = "meanf", name = "Mf" )
MeanFF	<- mxAlgebra(expression = cbind(Mf, Mf), name = "expMeanf")

# Define Matrices to estimate a, c, and e path coefficients for Males And Females
pathAm <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "am11", name = "am")
pathCm <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "cm11", name = "cm")
pathEm <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "em11", name = "em")
pathAf <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "af11", name = "af")
pathCf <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "cf11", name = "cf")
pathEf <- mxMatrix(type = "Full", nrow = nv, ncol = nv, free = TRUE, values = 0.6, label = "ef11", name = "ef")

# Matrices A, C, and E compute variance components
covAm	<- mxAlgebra(expression = am %*% t(am), name = "Am")
covCm	<- mxAlgebra(expression = cm %*% t(cm), name = "Cm")
covEm	<- mxAlgebra(expression = em %*% t(em), name = "Em")
covAf	<- mxAlgebra(expression = af %*% t(af), name = "Af")
covCf	<- mxAlgebra(expression = cf %*% t(cf), name = "Cf")
covEf	<- mxAlgebra(expression = ef %*% t(ef), name = "Ef")

# Algebra to compute total variances and standard deviations (diagonal only)
Varm <- mxAlgebra(expression = Am + Cm + Em, name = "Vm")
Varf <- mxAlgebra(expression = Af + Cf + Ef, name = "Vf")

# Algebra to compute standardized variance components
h2m	<- mxAlgebra(expression = Am/Vm, name = "hm2")
c2m	<- mxAlgebra(expression = Cm/Vm, name = "cm2")
e2m	<- mxAlgebra(expression = Em/Vm, name = "em2")
h2f	<- mxAlgebra(expression = Af/Vf, name = "hf2")
c2f	<- mxAlgebra(expression = Cf/Vf, name = "cf2")
e2f	<- mxAlgebra(expression = Ef/Vf, name = "ef2")
    
# Algebra for expected variance/covariance matrix in the 4 groups
covMZM <- mxAlgebra(expression = rbind(cbind(Am + Cm + Em, Am+Cm), cbind(Am + Cm, Am + Cm + Em)), name = "expCovMZM")
covMZF <- mxAlgebra(expression = rbind(cbind(Af + Cf + Ef, Af+Cf), cbind(Af + Cf, Af + Cf + Ef)), name = "expCovMZF")
covDZM <- mxAlgebra(expression = rbind(cbind(Am + Cm + Em, 0.5%x%Am + Cm), cbind(0.5%x%Am + Cm, Am + Cm + Em)), name = "expCovDZM")
covDZF <- mxAlgebra(expression = rbind(cbind(Af + Cf + Ef, 0.5%x%Af + Cf), cbind(0.5%x%Af + Cf, Af + Cf + Ef)), name = "expCovDZF")
    
# Data objects for Multiple Groups
dataMZM	<- mxData(observed = dat.twin.MZm, type = "raw")
dataDZM	<- mxData(observed = dat.twin.DZm, type = "raw")
dataMZF	<- mxData(observed = dat.twin.MZf, type = "raw")
dataDZF	<- mxData(observed = dat.twin.DZf, type = "raw")

# fit function
fitFunction <- mxFitFunctionML()
obj	<-mxFitFunctionAlgebra("m2LL")

# confidence intervals
ciM <- mxCI(c('hm2', 'cm2', 'em2'))
ciF <- mxCI(c('hf2', 'cf2', 'ef2'))
```

## Social isolation 

### Age 12

```{r select which variables to use}
# selvars_si12_chosen <- selvars_si12                 # raw
# selvars_si12_chosen <- selvars_si12_z_score         # standardised
# selvars_si12_chosen <- selvars_si12norm             # normalised
# selvars_si12_chosen <- selvars_si12_z_score_norm    # standardised and normalised
  selvars_si12_chosen <- selvars_si12norm_reg         # normalised and regressed sex
```

```{r fit het model for social isolation 12}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_si12_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_si12_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_si12_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_si12_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_isolation12	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for social isolation 12}
# Run
hetace_fit_isolation12 <- mxRun(hetace_isolation12, intervals = TRUE)
hetace_isolation12_summ <- summary(hetace_fit_isolation12)

# Table
hetace_isolation12_table <- ACEhet_esitmates_table(data = hetace_isolation12_summ,
                                                   variable = "Social isolation",
                                                   age = "12")
hetace_isolation12_table
```

```{r specify and run the sub-model homogeneity ACE model isolation 12}
homace_isolation12 <- mxModel(hetace_fit_isolation12, name = "homace")

homace_isolation12	<- omxSetParameters(homace_isolation12, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_isolation12	<- mxRun(homace_isolation12, intervals = TRUE)
homace_fit_isolation12_summ	<- summary(homace_fit_isolation12)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_isolation12_table <- ACEhet_esitmates_table(data = homace_fit_isolation12_summ,
                                                   variable = "Social isolation",
                                                   age = "12")
homace_isolation12_table

# compare het and hom
mxCompare(hetace_fit_isolation12, homace_fit_isolation12)
```

### Age 18

```{r select which variables to use}
# selvars_si18_chosen <- selvars_si18                 # raw
# selvars_si18_chosen <- selvars_si18_z_score         # standardised
# selvars_si18_chosen <- selvars_si18norm             # normalised
# selvars_si18_chosen <- selvars_si18_z_score_norm    # standardised and normalised
  selvars_si18_chosen <- selvars_si18norm_reg         # normalised and regressed sex
```

```{r fit het model for social isolation 18}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_si18_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_si18_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_si18_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_si18_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_isolation18	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for social isolation 18}
# Run
hetace_fit_isolation18 <- mxRun(hetace_isolation18, intervals = TRUE)
hetace_isolation18_summ <- summary(hetace_fit_isolation18)

# Table
hetace_isolation18_table <- ACEhet_esitmates_table(data = hetace_isolation18_summ,
                                                   variable = "Social isolation",
                                                   age = "18")
hetace_isolation18_table
```

```{r specify and run the sub-model homogeneity ACE model isolation 18}
homace_isolation18 <- mxModel(hetace_fit_isolation18, name = "homace")

homace_isolation18	<- omxSetParameters(homace_isolation18, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_isolation18	<- mxRun(homace_isolation18, intervals = TRUE)
homace_fit_isolation18_summ	<- summary(homace_fit_isolation18)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_isolation18_table <- ACEhet_esitmates_table(data = homace_fit_isolation18_summ,
                                                   variable = "Social isolation",
                                                   age = "18")
homace_isolation18_table

# compare het and hom
mxCompare(hetace_fit_isolation18, homace_fit_isolation18)
```

## Anxiety

### Age 12

```{r select which variables to use}
# selvars_anx12_chosen <- selvars_anx12                 # raw
# selvars_anx12_chosen <- selvars_anx12_z_score         # standardised
# selvars_anx12_chosen <- selvars_anx12norm             # normalised
# selvars_anx12_chosen <- selvars_anx12_z_score_norm    # standardised and normalised
  selvars_anx12_chosen <- selvars_anx12norm_reg         # normalised and regressed sex
```

```{r fit het model for anxiety 12}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_anx12_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_anx12_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_anx12_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_anx12_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_anxiety12	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for anxiety 12}
# Run
hetace_fit_anxiety12 <- mxRun(hetace_anxiety12, intervals = TRUE)
hetace_anxiety12_summ <- summary(hetace_fit_anxiety12)

# Table
hetace_anxiety12_table <- ACEhet_esitmates_table(data = hetace_anxiety12_summ,
                                                   variable = "Anxiety",
                                                   age = "12")
hetace_anxiety12_table
```

```{r specify and run the sub-model homogeneity ACE model anxiety 12}
homace_anxiety12 <- mxModel(hetace_fit_anxiety12, name = "homace")

homace_anxiety12	<- omxSetParameters(homace_anxiety12, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_anxiety12	<- mxRun(homace_anxiety12, intervals = TRUE)
homace_fit_anxiety12_summ	<- summary(homace_fit_anxiety12)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_anxiety12_table <- ACEhet_esitmates_table(data = homace_fit_anxiety12_summ,
                                                   variable = "Anxiety",
                                                   age = "12")
homace_anxiety12_table

# compare het and hom
mxCompare(hetace_fit_anxiety12, homace_fit_anxiety12)
```

### Age 18

```{r select which variables to use}
# selvars_anx18_chosen <- selvars_anx18                 # raw
# selvars_anx18_chosen <- selvars_anx18_z_score         # standardised
# selvars_anx18_chosen <- selvars_anx18norm             # normalised
# selvars_anx18_chosen <- selvars_anx18_z_score_norm    # standardised and normalised
  selvars_anx18_chosen <- selvars_anx18norm_reg         # normalised and regressed sex
```

```{r fit het model for anxiety 18}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_anx18_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_anx18_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_anx18_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_anx18_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_anxiety18	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for anxiety 18}
# Run
hetace_fit_anxiety18 <- mxRun(hetace_anxiety18, intervals = TRUE)
hetace_anxiety18_summ <- summary(hetace_fit_anxiety18)

# Table
hetace_anxiety18_table <- ACEhet_esitmates_table(data = hetace_anxiety18_summ,
                                                   variable = "Anxiety",
                                                   age = "18")
hetace_anxiety18_table
```

```{r specify and run the sub-model homogeneity ACE model anxiety 18}
homace_anxiety18 <- mxModel(hetace_fit_anxiety18, name = "homace")

homace_anxiety18	<- omxSetParameters(homace_anxiety18, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_anxiety18	<- mxRun(homace_anxiety18, intervals = TRUE)
homace_fit_anxiety18_summ	<- summary(homace_fit_anxiety18)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_anxiety18_table <- ACEhet_esitmates_table(data = homace_fit_anxiety18_summ,
                                                   variable = "Anxiety",
                                                   age = "18")
homace_anxiety18_table

# compare het and hom
mxCompare(hetace_fit_anxiety18, homace_fit_anxiety18)
```

## Depression

### Age 12

```{r select which variables to use}
# selvars_dep12_chosen <- selvars_dep12                 # raw
# selvars_dep12_chosen <- selvars_dep12_z_score         # standardised
# selvars_dep12_chosen <- selvars_dep12norm             # normalised
# selvars_dep12_chosen <- selvars_dep12_z_score_norm    # standardised and normalised
  selvars_dep12_chosen <- selvars_dep12norm_reg         # normalised and regressed sex
```

```{r fit het model for depression 12}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_dep12_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_dep12_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_dep12_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_dep12_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_depression12	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for depression 12}
# Run
hetace_fit_depression12 <- mxRun(hetace_depression12, intervals = TRUE)
hetace_depression12_summ <- summary(hetace_fit_depression12)

# Table
hetace_depression12_table <- ACEhet_esitmates_table(data = hetace_depression12_summ,
                                                   variable = "Depression",
                                                   age = "12")
hetace_depression12_table
```

```{r specify and run the sub-model homogeneity ACE model depression 12}
homace_depression12 <- mxModel(hetace_fit_depression12, name = "homace")

homace_depression12	<- omxSetParameters(homace_depression12, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_depression12	<- mxRun(homace_depression12, intervals = TRUE)
homace_fit_depression12_summ	<- summary(homace_fit_depression12)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_depression12_table <- ACEhet_esitmates_table(data = homace_fit_depression12_summ,
                                                   variable = "Depression",
                                                   age = "12")
homace_depression12_table

# compare het and hom
mxCompare(hetace_fit_depression12, homace_fit_depression12)
```

### Age 18

```{r select which variables to use}
# selvars_dep18_chosen <- selvars_dep18                 # raw
# selvars_dep18_chosen <- selvars_dep18_z_score         # standardised
# selvars_dep18_chosen <- selvars_dep18norm             # normalised
# selvars_dep18_chosen <- selvars_dep18_z_score_norm    # standardised and normalised
  selvars_dep18_chosen <- selvars_dep18norm_reg         # normalised and regressed sex
```

```{r fit het model for depression 18}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_dep18_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_dep18_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_dep18_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_dep18_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_depression18	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for depression 18}
# Run
hetace_fit_depression18 <- mxRun(hetace_depression18, intervals = TRUE)
hetace_depression18_summ <- summary(hetace_fit_depression18)

# Table
hetace_depression18_table <- ACEhet_esitmates_table(data = hetace_depression18_summ,
                                                   variable = "Depression",
                                                   age = "18")
hetace_depression18_table
```

```{r specify and run the sub-model homogeneity ACE model depression 18}
homace_depression18 <- mxModel(hetace_fit_depression18, name = "homace")

homace_depression18	<- omxSetParameters(homace_depression18, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_depression18	<- mxRun(homace_depression18, intervals = TRUE)
homace_fit_depression18_summ	<- summary(homace_fit_depression18)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_depression18_table <- ACEhet_esitmates_table(data = homace_fit_depression18_summ,
                                                   variable = "Depression",
                                                   age = "18")
homace_depression18_table

# compare het and hom
mxCompare(hetace_fit_depression18, homace_fit_depression18)
```

## Conduct disorder

### Age 12

```{r select which variables to use}
# selvars_con12_chosen <- selvars_con12                 # raw
# selvars_con12_chosen <- selvars_con12_z_score         # standardised
# selvars_con12_chosen <- selvars_con12norm             # normalised
# selvars_con12_chosen <- selvars_con12_z_score_norm    # standardised and normalised
  selvars_con12_chosen <- selvars_con12norm_reg         # normalised and regressed sex
```

```{r fit het model for conduct 12}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_con12_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_con12_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_con12_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_con12_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_conduct12	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for conduct 12}
# Run
hetace_fit_conduct12 <- mxRun(hetace_conduct12, intervals = TRUE)
hetace_conduct12_summ <- summary(hetace_fit_conduct12)

# Table
hetace_conduct12_table <- ACEhet_esitmates_table(data = hetace_conduct12_summ,
                                                   variable = "Conduct disorder",
                                                   age = "12")
hetace_conduct12_table
```

```{r specify and run the sub-model homogeneity ACE model conduct 12}
homace_conduct12 <- mxModel(hetace_fit_conduct12, name = "homace")

homace_conduct12	<- omxSetParameters(homace_conduct12, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_conduct12	<- mxRun(homace_conduct12, intervals = TRUE)
homace_fit_conduct12_summ	<- summary(homace_fit_conduct12)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_conduct12_table <- ACEhet_esitmates_table(data = homace_fit_conduct12_summ,
                                                   variable = "Conduct disorder",
                                                   age = "12")
homace_conduct12_table

# compare het and hom
mxCompare(hetace_fit_conduct12, homace_fit_conduct12)
```

### Age 18

```{r select which variables to use}
# selvars_con18_chosen <- selvars_con18                 # raw
# selvars_con18_chosen <- selvars_con18_z_score         # standardised
# selvars_con18_chosen <- selvars_con18norm             # normalised
# selvars_con18_chosen <- selvars_con18_z_score_norm    # standardised and normalised
  selvars_con18_chosen <- selvars_con18norm_reg         # normalised and regressed sex
```

```{r fit het model for conduct 18}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_con18_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_con18_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_con18_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_con18_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_conduct18	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for conduct 18}
# Run
hetace_fit_conduct18 <- mxRun(hetace_conduct18, intervals = TRUE)
hetace_conduct18_summ <- summary(hetace_fit_conduct18)

# Table
hetace_conduct18_table <- ACEhet_esitmates_table(data = hetace_conduct18_summ,
                                                   variable = "Conduct disorder",
                                                   age = "18")
hetace_conduct18_table
```

```{r specify and run the sub-model homogeneity ACE model conduct 18}
homace_conduct18 <- mxModel(hetace_fit_conduct18, name = "homace")

homace_conduct18	<- omxSetParameters(homace_conduct18, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_conduct18	<- mxRun(homace_conduct18, intervals = TRUE)
homace_fit_conduct18_summ	<- summary(homace_fit_conduct18)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_conduct18_table <- ACEhet_esitmates_table(data = homace_fit_conduct18_summ,
                                                   variable = "Conduct disorder",
                                                   age = "18")
homace_conduct18_table

# compare het and hom
mxCompare(hetace_fit_conduct18, homace_fit_conduct18)
```

## Psychotic experiences

### Age 12

```{r select which variables to use}
# selvars_psy12_chosen <- selvars_psy12                 # raw
# selvars_psy12_chosen <- selvars_psy12_z_score         # standardised
# selvars_psy12_chosen <- selvars_psy12norm             # normalised
# selvars_psy12_chosen <- selvars_psy12_z_score_norm    # standardised and normalised
  selvars_psy12_chosen <- selvars_psy12norm_reg         # normalised and regressed sex
```

```{r fit het model for psychosis 12}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_psy12_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_psy12_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_psy12_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_psy12_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_psychosis12	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for psychosis 12}
# Run
hetace_fit_psychosis12 <- mxRun(hetace_psychosis12, intervals = TRUE)
hetace_psychosis12_summ <- summary(hetace_fit_psychosis12)

# Table
hetace_psychosis12_table <- ACEhet_esitmates_table(data = hetace_psychosis12_summ,
                                                   variable = "Psychosis",
                                                   age = "12")
hetace_psychosis12_table
```

```{r specify and run the sub-model homogeneity ACE model psychosis 12}
homace_psychosis12 <- mxModel(hetace_fit_psychosis12, name = "homace")

homace_psychosis12	<- omxSetParameters(homace_psychosis12, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_psychosis12	<- mxRun(homace_psychosis12, intervals = TRUE)
homace_fit_psychosis12_summ	<- summary(homace_fit_psychosis12)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_psychosis12_table <- ACEhet_esitmates_table(data = homace_fit_psychosis12_summ,
                                                   variable = "Psychosis",
                                                   age = "12")
homace_psychosis12_table

# compare het and hom
mxCompare(hetace_fit_psychosis12, homace_fit_psychosis12)
```

### Age 18

```{r select which variables to use}
# selvars_psy18_chosen <- selvars_psy18                 # raw
# selvars_psy18_chosen <- selvars_psy18_z_score         # standardised
# selvars_psy18_chosen <- selvars_psy18norm             # normalised
# selvars_psy18_chosen <- selvars_psy18_z_score_norm    # standardised and normalised
  selvars_psy18_chosen <- selvars_psy18norm_reg         # normalised and regressed sex
```

```{r fit het model for psychosis 18}
# Objective objects for Multiple Groups     
objMZM <- mxExpectationNormal(covariance = "expCovMZM", means = "expMeanm", dimnames = selvars_psy18_chosen)
objDZM <- mxExpectationNormal(covariance = "expCovDZM", means = "expMeanm", dimnames = selvars_psy18_chosen)
objMZF <- mxExpectationNormal(covariance = "expCovMZF", means = "expMeanf", dimnames = selvars_psy18_chosen)
objDZF <- mxExpectationNormal(covariance = "expCovDZF", means = "expMeanf", dimnames = selvars_psy18_chosen)

# Combine Groups
parsm <- list(pathAm, pathCm, pathEm, covAm, covCm, covEm, Varm, h2m, c2m, e2m)
parsf <- list(pathAf, pathCf, pathEf, covAf, covCf, covEf, Varf, h2f, c2f, e2f)

modelMZM <- mxModel(parsm, MeanM, MeanMM, covMZM, dataMZM, objMZM, fitFunction, name = "MZM")
modelDZM <- mxModel(parsm, MeanM, MeanMM, covDZM, dataDZM, objDZM, fitFunction, name = "DZM")
modelMZF <- mxModel(parsf, MeanF, MeanFF, covMZF, dataMZF, objMZF, fitFunction, name = "MZF")
modelDZF <- mxModel(parsf, MeanF, MeanFF, covDZF, dataDZF, objDZF, fitFunction, name = "DZF")

minus2ll <-mxAlgebra(expression = MZM.objective + DZM.objective + MZF.objective + DZF.objective, name = "m2LL")

hetace_psychosis18	<-mxModel("univHetACE", parsm, parsf, modelMZM, modelDZM, modelMZF, modelDZF, minus2ll, obj, ciM, ciF) 
```

```{r run het model for psychosis 18}
# Run
hetace_fit_psychosis18 <- mxRun(hetace_psychosis18, intervals = TRUE)
hetace_psychosis18_summ <- summary(hetace_fit_psychosis18)

# Table
hetace_psychosis18_table <- ACEhet_esitmates_table(data = hetace_psychosis18_summ,
                                                   variable = "Psychosis",
                                                   age = "18")
hetace_psychosis18_table
```

```{r specify and run the sub-model homogeneity ACE model psychosis 18}
homace_psychosis18 <- mxModel(hetace_fit_psychosis18, name = "homace")

homace_psychosis18	<- omxSetParameters(homace_psychosis18, 
                                labels = c("am11", "cm11", "em11", "af11", "cf11", "ef11"), free = TRUE, values = 0.6,
                                newlabels = c("a11", "c11", "e11", "a11", "c11", "e11"))

homace_fit_psychosis18	<- mxRun(homace_psychosis18, intervals = TRUE)
homace_fit_psychosis18_summ	<- summary(homace_fit_psychosis18)

# parameter estimates (check that hf2,cf2 and ef2 are the same)
homace_psychosis18_table <- ACEhet_esitmates_table(data = homace_fit_psychosis18_summ,
                                                   variable = "Psychosis",
                                                   age = "18")
homace_psychosis18_table

# compare het and hom
mxCompare(hetace_fit_psychosis18, homace_fit_psychosis18)
```
